Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-09 paper/paper.tex
Summary stats

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The mean and standard deviation of the true and expected bias.}
\label{table_errors}
\centering
\begin{tabular}{|l||r|r|r|r|}
\hline
Question & Bias Type  & Mean  & Standard deviation \\ \hline
\hline
type 1   & true      &      &           \\ \hline
type 1   & expected  &      &           \\ \hline
type 2   & true      &      &           \\ \hline
type 2   & expected  &      &           \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The mean and standard deviation of the true and expected bias.}
\label{table_errors}
\centering
\begin{tabular}{|l||r|r|r|r|}
\hline
Question & Bias Type  & Mean  & Standard deviation \\ \hline
\hline
type 1   & true      & -0.032 & 0.0386 \\ \hline
type 1   & expected  & -0.010 & 0.022  \\ \hline
type 2   & true      & -1.836 & 0.374  \\ \hline
type 2   & expected  & -0.127 & 0.041  \\ \hline
\end{tabular}
\end{table}
